Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-23 draft.tex
expand explanation metrics

@@

			In order to determine if the explanations have the potential to be useful to an end

@@

>>>>

			The results of the LIME explainer are then summarized together on a per-feature basis
			and normalized to produce a decimal number between -1 and 1 for every feature. In this
			case, a negative value implies that the given feature pushed the result of the model
			in the negative direction (i.e. not fake), while a positive value indicates the
			opposite.

@@

			In order to assess if the explanations have the potential to be useful to an end

@@

			In order to contextualize the metrics, I will make the following definitions.
				\item Let \(S\) be the set of samples with \(s \in S\) as an element of the set.
				\item Let \(F\) be the set of features with \(f \in F\) as an element of the set.
				\item Let \(w_{fs}\) be the weight value of feature \(f\) of sample \(s\) as
					produced by the explainer.
				\item Let \(l_{s}\) be the correct label of the sample \(s\).
			The first metric I will define is the mean of the absolute values of the weights of
			the explanations, summarized along the sample axis, delivering one value per feature.
			I will further refer to this metric as importance, and it can be mathematically
			defined as follows:
			\[\frac{\sum_{s \in S} |w_{fs}|}{|S|}\]
			The second metric I will define is the average aggregate correctness on a per-feature
			basis, which I will further refer to as trust. The trust per feature can be defined as
			\[\frac{\sum_{s \in S} w_{fs}(2l_{s}-1)}{|S|}\]
